---
title: "Analysis of Cloze results"
format: 
  html: 
    toc: true
    toc-location: right
    html-math-method: katex
    number-sections: true
    code-fold: true
    other-links: 
      - text: OSF data raw
        href: https://osf.io/9vzk4/overview
bibliography: glottalization.bib
csl: apa.csl
---

```{r}
#| echo: false
#| output: false

library(dplyr) # for data manipulation, graphic, and data wrangling
library(tidyr) # for data manipulation
library(readr) # loading in data
library(stringr) # look for stuff in strings
library(reshape2) # for data manipulation
library(ggplot2) # for plotting
library(here) # for creating pathways relative to the top-level directory
library(remotes) # allows accessing github
# library(joeyr) # needed for the find_outliers function
library(ggokabeito) # colorblind friendly color based on Okabe-Ito scheme
library(stringdist) # calculate the orthographic distance from word.
library(yaml) # parses markdown documents
library(knitr) # used to create tables in quarto documents

# Loading in the dictionary
dictionary <- readr::read_csv(here::here("data", "raw", "cmudict.csv"))

dictionary <- dictionary |>
  tidyr::unite(
    pronunciation,
    2:29,
    sep = " ",
    na.rm = TRUE
  )

# loading in the results
# path to CSV files
path <- here::here("data", "raw", "cloze_results")

# List all CSV files in the directory
csv_files <- list.files(path = path, pattern = "\\.csv$", full.names = TRUE)

# Read all CSV files into a list of data frames
data_list <- lapply(csv_files, read.csv)

# Optionally, combine all data frames into one data frame
combined_data <- do.call(rbind, data_list)

cloze <- combined_data |>
  dplyr::mutate(
    target = as.character(stringr::str_extract_all(
      text,
      "(?<=%)[^%]+(?=%)",
      simplify = TRUE
    )),
    response = stringr::str_replace_all(
      response,
      pattern = '\\[|\\]|"',
      replacement = ''
    )
  ) |>
  dplyr::select(
    -c('study_id', 'session_id')
  ) |>
  dplyr::filter(block == "main") |>
  dplyr::mutate(
    response = stringr::str_to_lower(response),
    response = stringr::str_replace_all(response, "[[:punct:]]", ""),
    target = stringr::str_to_lower(target),
    in_dictionary = response %in% dictionary$entry,
    lev_dist = stringdist::stringdist(response, target, method = "lv")
  )
```

## Introduction

This page describes the results of a Cloze task, which is a technique in psycholinguistic studies to test for the predictability of words given a specific context [@snellReadersAreParallel2019; @miraultAlgorithmAnalyzingCloze2021]. This task was used to help compare the predictability of the target words used in a reading task about the role surprisal has on the pronunciation of t-glottalization and strengthening [@brinkerhoffTglottalizationStrengtheningAmerican2025]. 

## Methods
### Sentences

The sentences used in the cloze task were identical to the sentences used in the reading task from @brinkerhoffTglottalizationStrengtheningAmerican2025. The sentences were constructed for thirty target words in two different conditions. The words were selected from three phonological construction: (i) 10 words with word final /tn/ clusters, (ii) 10 words with the FAIL vowel precedinging a word final lateral, e.g., /e͡ɪl/, and (iii) 10 words with the FELL vowel preceding a word final lateral, e.g., /ɛl/. This wors were selected because of their claimed status as dialectal markers in Utahn English. These thirty words were placed in sentences constructed to minipulate the infomation load of the target word. The conditions were high information load and low information load.  

```{r}
# Unique ids for each sentence as they appear in the experiment, check if the entry is the dictionary
responses <- cloze |>
  dplyr::mutate(
    sentence_id = match(text, unique(text)),
    in_dictionary = response %in% dictionary$entry
  )

# Dataframe showing each sentence with its sentence_id
sentences <- responses |>
  dplyr::select(sentence_id, text) |>
  dplyr::distinct() |> 
  dplyr::mutate(
    info_load = c(
      "low",
      "high",
      "high",
      "low",
      "high",
      "low",
      "high",
      "low",
      "low",
      "high",
      "high",
      "low",
      "low",
      "high",
      "high",
      "low",
      "high",
      "low",
      "high",
      "high",
      "low",
      "high",
      "low",
      "low",
      "low",
      "low",
      "high",
      "high",
      "low",
      "high",
      "high",
      "high",
      "high",
      "high",
      "high",
      "low",
      "low",
      "high",
      "high",
      "high",
      "low",
      "high",
      "low",
      "low",
      "low",
      "low",
      "low",
      "high",
      "low",
      "low",
      "low",
      "low",
      "low",
      "low",
      "high",
      "high",
      "high",
      "low",
      "high",
      "high"
    )
  )
```
::: {.panel-tabset}

## Sentences from randomization A with id and information load
```{r}
knitr::kable(sentences[1:30,])
```

## Sentences from randomization B with id and information load
```{r}
knitr::kable(sentences[31:60,])
```

Sentences used in the cloze task their unique identification numbers
:::

## References

::: {#refs} 
:::